\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
resolve comments

Final Field a' : nat := 1.
Field c : a'@\YZ{should this be a'?}\EDJreply{Yes Thanks.}@ = 1 := eq_refl.
Field bop : nat -> nat -> nat := (+).
Fail Field comm_add : ...

@@

Override Field bop := (-).@\YZ{'add' is not a good choice of name---it doesn't make sense to override add with subtraction.}\EDJreply{Changed to b(inary)op now}@

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat -> nat@\YZ{nat -> nat ?}\EDJreply{Yes. Thanks}@ := (+ 1).
  Field p : monotonic f := ...
 EndFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}

@@

In our Coq plugin, we can achieve such exposure of definitional equality by
exposing the whole definition directly into the compiled module type. Doing so we also prohibit overriding because
subtraction doesn't have the same definition as $add$. We require the
users to decorate field as `Final' so that the plugin will proceed with
this special treatment.\YZ{This para is confusing: which kind of equality is used, propositional or judgmental? Where does 'Final' show up in the example?}\EDJreply{I rephrase it and remove the part on talking about meta-theory. Now everything is about judgemental so I don't have to emphasize judgemental. I wanted to make the example small but I guess I can add one `Final' statement into our example. Don't resolve it until I add it into Figure 2.}

>>>>

Final Field a' : nat := 1.
Field c : a' = 1 := eq_refl.
Field bop : nat -> nat -> nat := (+).
Fail Field comm_add : ...

@@

Override Field bop := (-).

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat -> nat := (+ 1).
  Field p : monotonic f := ...
 EndFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}

@@

In our Coq plugin, we can achieve such exposure of definitional equality by
exposing the whole definition directly into the compiled module type. Doing so we also prohibit overriding because
subtraction doesn't have the same definition as $add$. We require the
users to decorate field as `Final' so that the plugin will proceed with
this special treatment.
%\YZ{This para is confusing: which kind of equality is used, propositional or judgmental? Where does 'Final' show up in the example?}\EDJreply{I rephrase it and remove the part on talking about meta-theory. Now everything is about judgemental so I don't have to emphasize judgemental. I wanted to make the example small but I guess I can add one `Final' statement into our example. Don't resolve it until I add it into Figure 2.}
